### 2016-09-22 rebuttal.tex

We disagree with the reviewer on a few points. We do not consider SymPy Live
or SymPy Gamma to be key components of SymPy. The paper goal of the paper is
to primarily be about the SymPy library. While SymPy Live and SymPy Gamma are
maintained by the SymPy community, we consider them to be separate projects. A
mention of SymPy Live has been added to the introduction (see editor
point~\ref{editorpoint1}), as it may assist an interested reader in trying the
examples from the paper.

The ``Other Projects that
Depend on SymPy'' section (which has been renamed from ``Other Projects that
Use SymPy'') is {\color{red}TODO: Add reasons here, or else move this to the
paper as the reviewer requests.}

The ``Comparison with Mathematica'' section has been placed in the supplement
because we do not feel that a treatment in the main manuscript would be fair
without an equal comparison to other principle computer algebra systems, such
as Maple, SageMath, and Maxima. Unfortunately, our authorship is inexpert in
these systems, so a complete and fair comparison is impossible.

We are unclear why the reviewer has called out specific sections over others
for his suggested reorganization. We deep all the sections in section 3 (now
section 2) to be important core components of the library. Regarding the supplement
sections (previously) 5, 7, and 9---``Sets'', ``Category Theory'', and ``SymPy
Live'', respesctively---only set sets module is potentially applicable to the
wider audience of the main paper. However, in SymPy 1.0, the sets module is
still in a relatively infant stage. It is mentioned already in conjunction
with the \texttt{solveset} function. We have added some additional text to the
solvers subsection regarding \texttt{sympy.sets}. The category theory module
in SymPy is very domain specific, and independent of other SymPy modules. We
consider the module too niche to warrant expanding upon in the main
manuscript. SymPy Live, as has been discussed above, is not a SymPy submodule.
It is a separate project from the SymPy library. It would be inappropriate to
list it alongside the features of SymPy.

We also consider the supplement sections (previously) 2, 3, 4, and
6---''Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript. The
``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.
The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the logic module discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the future
work section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

The ``Solvers'' subsection already mentions that SymPy can solve Diophantine
equations. We consider this specific application to be niche enough to keep
the discussion in the supplement. We have added a reference to the supplement
to the ``Solvers'' subsection. The ``Statistics'' module is an independent
submodule (no other SymPy submodules depend on it). We do not consider it to
be a core module of SymPy.

### 2016-09-22 rebuttal.tex

We also consider the supplement sections (previously) 2, 3, 4, and
6---''Series'', ``Logic'', ``Diophantine Equations'', and ``Statistics'',
respectively---to be in depth beyond the goals of the main manuscript. The
``Series'' section discusses relatively advanced series expansion methods. We
have added a paragraph detailing basic series expansion to the ``Calculus''
subsection, with a reference to the more detailed section in the supplement.
The ``Logic'' section is alluded to in the ``Assumptions'' subsection, but is
not discussed in depth in the main manuscript. While the logic submodule is
indeed important for certain parts of SymPy, particularly the assumptions, we
do not consider it to be of interest to the general reader. Furthermore, on a
technical note, the assumptions discussed in the manuscript are the so-called
``old assumptions'', and do not use the logic module discussed in the
supplement. The so-called ``new assumptions'', mentioned briefly in the future
work section, does use it, but we have opted to not discuss this module in
depth, as it is still in development and not fully usable.

The ``Solvers'' subsection already mentions that SymPy can solve Diophantine
equations. We consider this specific application to be niche enough to keep
the discussion in the supplement. We have added a reference to the supplement
to the ``Solvers'' subsection. The ``Statistics'' module is an independent
submodule (no other SymPy submodules depend on it). We do not consider it to
be a core module of SymPy.

We feel the architecture is one of the most important parts of the paper. The
goal of the paper is to discuss the architecture core features of SymPy. We
therefore strongly feel that this section belongs in the main manuscript, and
not the supplementary material. We have followed the reviewer's advice and
moved the architecture section to the end of the paper, to make the paper
easier to follow.
\end{solution}
\end{questions}

### 2016-09-23 other_projects_that_use_sympy.tex
Remove some of the "other projects that use SymPy"

\begin{itemize}
\item
  \href{http://cadabra.science/index.html}{\textbf{Cadabra}}: Cadabra is
  a CAS designed specifically for the
  resolution of problems encountered in field theory.
\item
  \href{http://octave.sourceforge.net/symbolic/}{\textbf{Octave Symbolic}}:
  The Octave-Forge Symbolic package adds symbolic calculation features
  to GNU Octave. These include common CAS tools such
  as algebraic operations, calculus, equation solving, Fourier and
  Laplace transforms, variable precision arithmetic, and other features.
\item
  \href{https://github.com/jverzani/SymPy.jl}{\textbf{SymPy.jl}}:
  Provides a Julia interface to SymPy using PyCall.
\item
  \href{https://mathics.github.io/}{\textbf{Mathics}}: Mathics is a
  free, general-purpose online CAS featuring Mathematica compatible
  syntax and functions. It is backed by highly extensible Python code,
  relying on SymPy for most mathematical tasks.
\item
  \href{http://mathpix.com/}{\textbf{Mathpix}}: An iOS App, that detects handwritten math as input, and uses
  SymPy Gamma to evaluate the math input and generate the relevant
  steps to solve the problem.
\item
  \href{http://openrave.org/docs/0.8.2/openravepy/ikfast/}{\textbf{IKFast}}:
  IKFast is a robot kinematics compiler provided by
  \href{http://openrave.org/}{OpenRAVE}. It analytically solves robot inverse
  kinematics equations and generates optimized C++ files. It uses SymPy for
  its internal symbolic mathematics.
\item
  \href{http://www.sagemath.org/}{\textbf{Sage}}: A CAS, visioned to be
  a viable free open source alternative to Magma, Maple, Mathematica and
  MATLAB\@. Sage includes many open source mathematical libraries, including
  SymPy.
\item
  \href{https://cloud.sagemath.com}{\textbf{SageMathCloud}}:
  SageMathCloud is a web-based cloud computing and course management
  platform for computational mathematics.
\item
  \href{http://www.pydy.org/}{\textbf{PyDy}}: Multibody Dynamics with
  Python.
\item
  \href{https://github.com/brombo/galgebra}{\textbf{galgebra}}:
  Geometric algebra (previously \texttt{sympy.galgebra}).
\item
  \href{http://yt-project.org/}{\textbf{yt}}: Python package for
  analyzing and visualizing volumetric data (\texttt{yt.units} uses SymPy).
\item
  \href{http://sfepy.org/}{\textbf{SfePy}} (Simple finite elements in Python),
  cf.~\cite{cimrman2014sfepy}, is a Python package for solving partial
  differential equations (PDEs) in 1D, 2D and 3D by the finite element (FE)
  method~\cite{Zienkiewicz2013FEM}. SymPy is used within this package mostly for
  code generation and testing.
\item
  \href{http://quameon.sourceforge.net/}{\textbf{Quameon}}: Quantum
  Monte Carlo in Python.
\item
  \href{http://lcapy.elec.canterbury.ac.nz/}{\textbf{Lcapy}}:
  Experimental Python package for teaching linear circuit analysis.
\item
  \href{http://digitalcommons.calpoly.edu/cgi/viewcontent.cgi?article=1072\&context=physsp/}{\textbf{Quantum
  Programming in Python}}: Quantum 1D Simple Harmonic Oscillator and
  Quantum Mapping Gate.
\item
  \href{http://mech.fsv.cvut.cz/~stransky/software/latexexpr/doc/}{\textbf{LaTeX
  Expression project}}: Easy \LaTeX{} typesetting of algebraic expressions
  in symbolic form with automatic substitution and result computation.
\item
  \href{https://www.researchgate.net/publication/260585491_Symbolic_Statistics_with_SymPy/}{\textbf{Symbolic
  statistical modeling}}: Adding statistical operations to complex
  physical models.
\end{itemize}

>>>>

\begin{itemize}
\item
  \href{http://cadabra.science/index.html}{\textbf{Cadabra}}: Cadabra is
  a CAS designed specifically for the
  resolution of problems encountered in field theory.
\item
  \href{http://octave.sourceforge.net/symbolic/}{\textbf{Octave Symbolic}}:
  The Octave-Forge Symbolic package adds symbolic calculation features
  to GNU Octave. These include common CAS tools such
  as algebraic operations, calculus, equation solving, Fourier and
  Laplace transforms, variable precision arithmetic, and other features.
\item
  \href{https://github.com/jverzani/SymPy.jl}{\textbf{SymPy.jl}}:
  Provides a Julia interface to SymPy using PyCall.
\item
  \href{https://mathics.github.io/}{\textbf{Mathics}}: Mathics is a
  free, general-purpose online CAS featuring Mathematica compatible
  syntax and functions. It is backed by highly extensible Python code,
  relying on SymPy for most mathematical tasks.
\item
  \href{http://mathpix.com/}{\textbf{Mathpix}}: An iOS App, that detects handwritten math as input, and uses
  SymPy Gamma to evaluate the math input and generate the relevant
  steps to solve the problem.
\item
  \href{http://openrave.org/docs/0.8.2/openravepy/ikfast/}{\textbf{IKFast}}:
  IKFast is a robot kinematics compiler provided by
  \href{http://openrave.org/}{OpenRAVE}. It analytically solves robot inverse
  kinematics equations and generates optimized C++ files. It uses SymPy for
  its internal symbolic mathematics.
\item
  \href{http://www.sagemath.org/}{\textbf{Sage}}: A CAS, visioned to be
  a viable free open source alternative to Magma, Maple, Mathematica and
  MATLAB\@. Sage includes many open source mathematical libraries, including
  SymPy.
\item
  \href{https://cloud.sagemath.com}{\textbf{SageMathCloud}}:
  SageMathCloud is a web-based cloud computing and course management
  platform for computational mathematics.
\item
  \href{http://www.pydy.org/}{\textbf{PyDy}}: Multibody Dynamics with
  Python.
\item
  \href{https://github.com/brombo/galgebra}{\textbf{galgebra}}:
  Geometric algebra (previously \texttt{sympy.galgebra}).
\item
  \href{http://yt-project.org/}{\textbf{yt}}: Python package for
  analyzing and visualizing volumetric data (\texttt{yt.units} uses SymPy).
\item
  \href{http://sfepy.org/}{\textbf{SfePy}} (Simple finite elements in Python),
  cf.~\cite{cimrman2014sfepy}, is a Python package for solving partial
  differential equations (PDEs) in 1D, 2D and 3D by the finite element (FE)
  method~\cite{Zienkiewicz2013FEM}. SymPy is used within this package mostly for
  code generation and testing.
\item
  \href{http://quameon.sourceforge.net/}{\textbf{Quameon}}: Quantum
  Monte Carlo in Python.
\item
  \href{http://lcapy.elec.canterbury.ac.nz/}{\textbf{Lcapy}}:
  Experimental Python package for teaching linear circuit analysis.
\end{itemize}
